Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-14 results.tex
improved figure 7 and renamed 12 to 14
rename to new figures 12 and 13
rename to new figures 10 and 11

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-10.pdf} 
    \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 5 using the combined model (R,U) hazard calculations. Mean expected values are shown in the middle, whereas the top and bottom frames correspond to the results obtained using plus and minus one standard deviation.}
    \label{fig:pga.ru.std}
\end{figure*}

@@

@@

\begin{figure*}[th!]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-11} 
    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U). \myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
    \label{fig:hazardcurve}
\end{figure*}

\myrevision{
We also note that the overall distribution of mean PGA pattern agrees with the recent study by \citet{Khodaverdian_2016_BSSA}. However, in general, their results are slightly lower than this study. They provided a rough estimate of the PGA, and the seismicity parameters, like completeness magnitude, the catalog, $M_{max}$, and $b-value$ are different in these two studies.  Consequently, we don't expect to match the results. For example  in case of $b-value$, in the same study region, \citet{Khodaverdian_2016_BSSA} reported very high variation of $b-value$ (0.56 - 1.27).  56\% of grid points have $b-value > 1$ and 53 \% of them are greater than 1.1.  Where in this study the $b-value$ has a narrow range of variation (0.93-1.15).  These estimates also agree, on average, with other studies. For the Azerbaijan tectonic seismic region for the city of Uremia, we found 0.24 g which is slightly lower than \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for 10 \% probability of exceedance in 50 years. For a 2\% probability of exceedance in 50 years, \citet{Golara2014} expected acceleration on the order of 0.3 - 0.5 g, where or mean value is 0.38 g. For the city of Tabriz, the results match with \citet{BHRC2014} and are in the range of \citet{Zare2012} for 10 \% probability of exceedance in 50 years.  \citet{Vafaie2011} expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% probability of exceedance in 50 years, respectively, where our mean values are about 0.61 and 0.35 g for the same corresponding probabilities. For the city of Ardabil, we found 0.73 g and 0.43 g for 2 and 10\% probability of exceedance in 50 years.  Our results are slightly higher than \citet{BHRC2014}, however, for 10\% probability of exceedance in 50 years, the results are in the range reported by \citet{Zare2012}. For 2\% probability of exceedance in 50 years, our results are very close to \citet{Golara2014} and \citet{Khodaverdian_2016_BSSA}. In the Alborz tectonic seismic region for the city of Rasht, our results are in a well agreement with the recent study of \citet{Abdollahzadeh2014}. For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Za2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years. For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian2015}. For the Kopeh Dagh tectonic seismic region for the city of Mashhad, results are lower than \citet{BHRC2014} and higher than \citet{Khodaverdian_2016_BSSA}.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-12} 
    \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran. Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively. Also the PGA ranges of the \ref{tab:pga} are represented. The shaded area represents the upper and lower value of uncertainty at the GMPEs.}
    \label{fig:tehran}
\end{figure}
\myrevision{
Last, we put additional attention on the results for the capital city of Tehran. We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years. Our results are similar to those obtained by \citet{Boostan2015} in the range between 0.1 and 0.3 g (corresponding to annual probabilities of exceedance between $10^{-3}$ and $10^{-1}$), and then it is in the mean range of the mentioned studies.  Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}. Expected PGA range of other studies mentioned at the \ref{tab:pga}, represents, on average, our study presents trustable results. The shaded area, represents the upper and lower value of uncertainty at the GMPEs. In other word the upper part edge is calculated by just considering GMPEs+Unc  and the lower edge is calculated by just considering GMPEs-Unc. It perfectly represents that almost all studies are in the range of uncertainty of the GMPEs, and using one appropriate backbone GMPE as well as the uncertainties could have better role in considering the epistemic uncertainty than using multiple GMPEs as \citet{Atkinson2014} concluded.}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-12.pdf}
    \caption{Expected PGA values throughout the region of interest for 2 (left) and 10 (right) percent probability of exceeding an earthquake magnitude $M_w$ 5 using the combined model (R,U) hazard calculations. Mean expected values are shown in the middle, whereas the top and bottom frames correspond to the results obtained using plus and minus one standard deviation.}
    \label{fig:pga.ru.std}
\end{figure*}

@@

\begin{figure*}%[h!]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-13}
    \caption{Hazard curves representing the annual probability of exceedance as function of peak ground acceleration for six cities in northern Iran based on the two basic models considered in this study, R and U, and the combined model (R,U). \myrevision{Dashed lines represent the 0.0021 and 0.000404 annual probability of exceedance corresponding to probability of exceedance of 10 and 2 percent in 50 years.}}
    \label{fig:hazardcurve}
\end{figure*}

@@

\myrevision{%
We also note that the overall distribution of mean PGA pattern agrees with the recent study by \citet{Khodaverdian_2016_BSSA}. However, in general, their results are slightly lower than this study. They provided a rough estimate of the PGA, and the seismicity parameters, like completeness magnitude, the catalog, $M_{max}$, and $b-value$ are different in these two studies.  Consequently, we don't expect to match the results. For example  in case of $b-value$, in the same study region, \citet{Khodaverdian_2016_BSSA} reported very high variation of $b-value$ (0.56 - 1.27).  56\% of grid points have $b-value > 1$ and 53 \% of them are greater than 1.1.  Where in this study the $b-value$ has a narrow range of variation (0.93-1.15).  These estimates also agree, on average, with other studies. For the Azerbaijan tectonic seismic region for the city of Uremia, we found 0.24 g which is slightly lower than \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for 10 \% probability of exceedance in 50 years. For a 2\% probability of exceedance in 50 years, \citet{Golara2014} expected acceleration on the order of 0.3 - 0.5 g, where or mean value is 0.38 g. For the city of Tabriz, the results match with \citet{BHRC2014} and are in the range of \citet{Zare2012} for 10 \% probability of exceedance in 50 years.  \citet{Vafaie2011} expected accelerations on the order of 0.30--0.90 and 0.20--0.65 g for 2 and 10\% probability of exceedance in 50 years, respectively, where our mean values are about 0.61 and 0.35 g for the same corresponding probabilities. For the city of Ardabil, we found 0.73 g and 0.43 g for 2 and 10\% probability of exceedance in 50 years.  Our results are slightly higher than \citet{BHRC2014}, however, for 10\% probability of exceedance in 50 years, the results are in the range reported by \citet{Zare2012}. For 2\% probability of exceedance in 50 years, our results are very close to \citet{Golara2014} and \citet{Khodaverdian_2016_BSSA}. In the Alborz tectonic seismic region for the city of Rasht, our results are in a well agreement with the recent study of \citet{Abdollahzadeh2014}. For the city of Tehran, the results are in agreement with \citet{Abdi2013}, and slightly lower than  \citet{BHRC2014}, \citet{Za2012}, and \citet{Golara2014} for 10\% probability of exceedance in 50 years. For 2\% 10\% probability of exceedance in 50 years, our results are lower than \citet{Golara2014} and higher than \citet{Khodaverdian2015}. For the Kopeh Dagh tectonic seismic region for the city of Mashhad, results are lower than \citet{BHRC2014} and higher than \citet{Khodaverdian_2016_BSSA}.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-14}
    \caption{Hazard curve comparison between the models considered in this study and the results of two previous studies by \citet{Ghodrati2003} and \citet{Boostan2015} for the city of Tehran. Here, the two previous studies just mentioned are identified with the codes Gh03 and Bo15, respectively. Also the PGA ranges of the \ref{tab:pga} are represented. The shaded area represents the upper and lower value of uncertainty at the GMPEs.}
    \label{fig:tehran}
\end{figure}

\myrevision{%
Last, we put additional attention on the results for the capital city of Tehran. We compare hazard curves obtained in this study against those computed by \citet{Ghodrati2003} and \citet{Boostan2015} as well as ranges from other studies for 2 and 10\% probability of exceedance in 50 years. Our results are similar to those obtained by \citet{Boostan2015} in the range between 0.1 and 0.3 g (corresponding to annual probabilities of exceedance between $10^{-3}$ and $10^{-1}$), and then it is in the mean range of the mentioned studies.  Conversely, the trend in the hazard curve from \citet{Boostan2015} suggest the city is to expect significantly higher levels of ground motion at higher probability rates, which is contrary to our findings and those of \citet{Ghodrati2003}. Expected PGA range of other studies mentioned at the \ref{tab:pga}, represents, on average, our study presents trustable results. The shaded area, represents the upper and lower value of uncertainty at the GMPEs. In other word the upper part edge is calculated by just considering GMPEs+Unc  and the lower edge is calculated by just considering GMPEs-Unc. It perfectly represents that almost all studies are in the range of uncertainty of the GMPEs, and using one appropriate backbone GMPE as well as the uncertainties could have better role in considering the epistemic uncertainty than using multiple GMPEs as \citet{Atkinson2014} concluded.}
